---
title: "Thesis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
r = getOption("repos")
r["CRAN"] = "http://cran.us.r-project.org"
options(repos = r)
library(tidyverse)
library(dplyr)
library(summarytools)
library(sjPlot)
library(afex)
library(emmeans)
library(psych)
library(car)
library(ggplot2)
library(readxl)
library(ggpubr)
library(readxl)
library(stargazer)
library(moments)
library(plotly)
library(plm)
library(foreign)
library(lmtest)
library(lubridate)
library(DescTools)
install.packages("caret")
library(caret)
library(lmtest)
library(lubridate)
install.packages("ggpubr")
library(ggpubr)
library(sjPlot)
install.packages("formattable")
library(formattable)
install.packages("gridExtra")
library(gridExtra)
install.packages("extrafont")
library(extrafont)
font_import()
loadfonts(device="win") 
library(plotly)
install.packages("ncdf4")
library(ncdf4) 
install.packages("raster")
library(raster)
```

## Heat wave number - graph


```{r}
library(readxl)
Heat_Waves_NL <- read_excel("Heat_Waves_NL.xlsx", 
    sheet = "No heat waves")
View(Heat_Waves_NL)
figure1<-ggbarplot(Heat_Waves_NL, "Period", "N° of heat Waves",
 fill = "steelblue", color = "steelblue",
 label = TRUE, lab.pos = "in", lab.col = "white")
  geom_hline(yintercept = 0, linetype = 2, color = "lightgray")
  
figure1 + labs(title = "Heatwaves registered at De Bilt station", x = "Period", y = "Number of Heatwaves", caption = "Data: KNMI", color = "steelblue", family="A") +theme(text=element_text(family="A", face="bold", size=12))
```


## Warmgetallen

```{r}
getallen <- data.frame(Year=c("2006", "2018", "1995", "1976", "1947", "1994","2020","1983","2003","2019"),
   Warmgetallen=c(201.3, 196.0, 169.7, 163.8, 159.2, 147.9, 145.6, 133.9, 133.4, 130.9))


figure2<-ggbarplot(getallen, "Year", "Warmgetallen",
 fill = "steelblue", color = "steelblue",
 label = TRUE, lab.pos = "out", lab.col = "white")
  geom_hline(yintercept = 0, linetype = 2, color = "lightgray")
  
figure2 + labs(title = "Warmgetallen registered at De Bilt station", x = "Year", y = "Warmgetallen", caption = "Data: KNMI", color = "steelblue", family="A") +theme(text=element_text(family="A", face="bold", size=12))
```

## Average temperatures registered

#create matrix with 4 columns

```{r}
tab <- data.frame(Rank=c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"),
                  Year=c("2020", "2014", "2018", "2019", "2007", "2006", "2017", "2015", "2011", "2000"),
                  Average_Temperature=c(11.7, 11.7, 11.3, 11.2, 11.2, 11.2, 10.9, 10.9, 10.9, 10.9))

figure3<-as.data.frame(tab)
figure3

figure3<-formattable(tab, align =c("l","c","c"), 
            list(`Indicator Name` = formatter(
              "span", style = ~ style(color = "grey",font.weight = "bold")) 
))
lol<-tableGrob(tab)

lol
View(tab)
```

#### CO2 at Mauna Loa

```{r}
library(readxl)
co2 <- read_excel("co2.xlsx")
View(co2)


p1 <- ggplot() + geom_line(aes(y = Mean, x = Year),
                 data = co2)
windowsFonts(A = windowsFont("Times New Roman"))
p1

p1 + labs(title = "CO2 in dry air at NOAA’s Mauna Loa Observatory in ppm", x = "Year", y = "Mean CO2 ppm", caption = "Data: gml.noaa.gov", color = "steelblue", family="A") +theme(text=element_text(family="A", face="bold", size=12))

```

## Temperature

```{r}
temperature <- read_csv("temperature.csv")
View(temperature)

temperature$Time<-substr(temperature$Time,1,nchar(temperature$Time)-3)
temperature<-temperature[!duplicated(temperature$Time), ]
temperature$Time<-as.numeric(temperature$Time)
str(temperature)

temp<-ggplot(temperature, aes(x=temperature$Time, y=temperature$`Anomaly (deg C)`, group=1)) +
  geom_line( color="steelblue", size=0.1, alpha=0, linetype=2) + geom_smooth()+
  geom_hline(yintercept=0, linetype="dashed", 
                color = "black", size=0.5) 

temp + labs(title = "Temperature Anomaly (°C from 1961-1990 mean)", x = "Year", y = "Temperature Anomaly (smoothed)", caption = "Data: www.cru.uea.ac.uk", color = "steelblue", family="A") + theme(text=element_text(family="A", face="bold", size=12))


```

## try to get average temperature in NL

```{r}
library(readxl)
nltemp <- read_excel("nltemp.xlsx")
View(nltemp)
figure4<-ggplot(nltemp, aes(x=nltemp$Category))  + 
  geom_line(aes(y = nltemp$`5-yr smooth`), color="steelblue", size=1.5) +
  geom_hline(yintercept = mean(nltemp$`Annual Mean`), color="darkred", linetype="twodash")+annotate("text", min(nltemp$Category), 9.6, vjust=-1, label = "Average")

figure4 + labs(title = "Annual Mean Temperature of The Netherlands 1901-2020", x = "Year", y = "Temperature (in °C, 5-yr smooth)", caption = "Data: Climate Change Knowledge Portal", color = "steelblue", family="A") + theme(text=element_text(family="A", face="bold", size=12))
```



#### CREATE STUDY SUMMARY FOR LITERATURE

```{r}
library(sjPlot)
summarystudy <- read_excel("summarystudy.xlsx")
View(summarystudy)

tab_df(summarystudy,
file="sjt_des.doc")sjt

#create APA table for heat stress levels
library(sjPlot)
heatstresslevels <- read_excel("heat stress levels.xlsx")
View(heatstresslevels)

tab_df(heatstresslevels,
file="heat_des.doc")
```


#### CHeck the dataset
```{r}
library(haven)
dataset <- read_sas("nvm_data_tbv_mu_85_17.sas7bdat", 
    NULL)
View(dataset)

#filter data set to have noord holland, south holland and Utrecht Provinces
Brabant <- filter(dataset,dataset$obj_prov_ID ==7 | dataset$obj_prov_ID== 8| dataset$obj_prov_ID== 9)
# reduce dataset to only include obs. after 2000-01-01
Bra_2000 <- filter(Brabant, Brabant$obj_hid_DATUM_AANMELDING > "2000-01-01")

# format "Datum afmelding" as.date
Bra_1 <- Bra_2000
Bra_1$obj_hid_DATUM_AFMELDING <- as.Date(Bra_1$obj_hid_DATUM_AFMELDING, format= "%Y.%m.%d")
Bra_1$date <- as.Date(Bra_1$obj_hid_DATUM_AFMELDING)

#delete all NA's from the set
Bra_2 <- na.omit(Bra_1)

##create boxplot to see if there are outliers

boxplot(Bra_2$obj_hid_TRANSACTIEPRIJS)

# Remove outliers for house price
Bra_3 <- Bra_2[Bra_2$obj_hid_TRANSACTIEPRIJS < quantile(Bra_2$obj_hid_TRANSACTIEPRIJS, p = 0.99) & 
                   Bra_2$obj_hid_TRANSACTIEPRIJS > quantile(Bra_2$obj_hid_TRANSACTIEPRIJS, p = 0.01),] 

Bra_4 <- Bra_3[Bra_3$obj_hid_M2 < quantile(Bra_3$obj_hid_M2, p = 0.99) & 
                   Bra_3$obj_hid_M2 > quantile(Bra_3$obj_hid_M2, p = 0.01),] 

Bra_5 <- Bra_4[Bra_4$obj_hid_NKAMERS < quantile(Bra_4$obj_hid_NKAMERS, p = 0.99) & 
                   Bra_4$obj_hid_NKAMERS > quantile(Bra_4$obj_hid_NKAMERS, p = 0.01),] 

Bra_6 <- Bra_5[Bra_5$obj_hid_PERCEEL < quantile(Bra_5$obj_hid_PERCEEL, p = 0.99) & 
                   Bra_5$obj_hid_PERCEEL > quantile(Bra_5$obj_hid_PERCEEL, p = 0.01),] 

Bra_7 <- Bra_6[Bra_6$obj_hid_INHOUD < quantile(Bra_6$obj_hid_INHOUD, p = 0.99) & 
                   Bra_6$obj_hid_INHOUD > quantile(Bra_6$obj_hid_INHOUD, p = 0.01),]

Bra_8 <- Bra_7[Bra_7$obj_hid_NVERDIEP < quantile(Bra_7$obj_hid_NVERDIEP, p = 0.99) & 
                   Bra_7$obj_hid_NVERDIEP > quantile(Bra_7$obj_hid_NVERDIEP, p = 0.01),]

Bra_9 <- Bra_8[Bra_8$obj_hid_NWC < quantile(Bra_8$obj_hid_NWC, p = 0.99) & 
                   Bra_8$obj_hid_NWC > quantile(Bra_8$obj_hid_NWC, p = 0.01),]

Bra_10 <- Bra_9[Bra_9$obj_hid_NKAMERS < quantile(Bra_9$obj_hid_NKAMERS, p = 0.99) & 
                   Bra_9$obj_hid_NKAMERS > quantile(Bra_9$obj_hid_NKAMERS, p = 0.01),]

Bra_11 <- Bra_10[Bra_10$obj_hid_BWPER < quantile(Bra_10$obj_hid_BWPER, p = 0.99) & 
                   Bra_10$obj_hid_BWPER > quantile(Bra_10$obj_hid_BWPER, p = 0.01),]


plot(Bra_11$obj_hid_PERCEEL)
# add transactieprijs variable with a log function 
Bra_11$lprice <- log(Bra_11$obj_hid_TRANSACTIEPRIJS)
# add m2 with log function
Bra_11$lm2 <- log(Bra_11$obj_hid_M2)

# correlation matrices 
# source: http://www.sthda.com/english/wiki/correlation-matrix-a-quick-start-guide-to-analyze-
#          format-and-visualize-a-correlation-matrix-using-r-software
         
space <- Bra_11[, c(13:16)]
cor_space <- cor(space)
round(cor_space, 2)
corrplot::corrplot(cor_space, method = "shade", type = "upper", title = "Space Correlation", tl.col = "black", 
                   tl.srt = 45)

#space
colnames(cor_space)[colnames(cor_space) == "obj_hid_M2"] <- "m2"
rownames(cor_space)[rownames(cor_space) == "obj_hid_M2"] <- "m2"
colnames(cor_space)[colnames(cor_space) == "obj_hid_PERCEEL"] <- "plot"
rownames(cor_space)[rownames(cor_space) == "obj_hid_PERCEEL"] <- "plot"
colnames(cor_space)[colnames(cor_space) == "obj_hid_WOONOPP"] <- "living"
rownames(cor_space)[rownames(cor_space) == "obj_hid_WOONOPP"] <- "living"
colnames(cor_space)[colnames(cor_space) == "obj_hid_INHOUD"] <- "volume"
rownames(cor_space)[rownames(cor_space) == "obj_hid_INHOUD"] <- "volume" 


rooms <- Bra_11[, c(37,43,49,50,51,52)]
cor_rooms <- cor(rooms)
round(cor_rooms, 2)
corrplot::corrplot(cor_rooms, method = "shade", type = "upper", title = "Rooms Correlation", tl.col = "black", 
                  tl.srt = 45)

#rooms
colnames(cor_rooms)[colnames(cor_rooms) == "obj_hid_NKAMERS"] <- "#rooms"
rownames(cor_rooms)[rownames(cor_rooms) == "obj_hid_NKAMERS"] <- "#rooms"
colnames(cor_rooms)[colnames(cor_rooms) == "obj_hid_WOONKA"] <- "#livingrooms"
rownames(cor_rooms)[rownames(cor_rooms) == "obj_hid_WOONKA"] <- "#livingrooms"
colnames(cor_rooms)[colnames(cor_rooms) == "obj_hid_NKEUKEN"] <- "#kitchens"
rownames(cor_rooms)[rownames(cor_rooms) == "obj_hid_NKEUKEN"] <- "#kitchens"
colnames(cor_rooms)[colnames(cor_rooms) == "obj_hid_NBIJKEUK"] <- "scullery"
rownames(cor_rooms)[rownames(cor_rooms) == "obj_hid_NBIJKEUK"] <- "scullery"
colnames(cor_rooms)[colnames(cor_rooms) == "obj_hid_NWC"] <- "#toilets"
rownames(cor_rooms)[rownames(cor_rooms) == "obj_hid_NWC"] <- "#toilets"
colnames(cor_rooms)[colnames(cor_rooms) == "obj_hid_NBADK"] <- "#bathrooms"
rownames(cor_rooms)[rownames(cor_rooms) == "obj_hid_NBADK"] <- "#bathrooms"
```
### ####### Dummy variable creation ########
```{r}
# apartment dummy: 0 if house categorie, 1 if apartment
Bra_11$apartment <- if_else(Bra_11$obj_hid_CATEGORIE == 2, 1, 0)
# building period dummies: base period is 1906-1931
Bra_11$construction_1500_1905 <- if_else(Bra_11$obj_hid_BWPER == 1, 1, 0)
Bra_11$construction_1931_1944 <- if_else(Bra_11$obj_hid_BWPER == 3, 1, 0)
Bra_11$construction_1945_1959 <- if_else(Bra_11$obj_hid_BWPER == 4, 1, 0)
Bra_11$construction_1960_1970 <- if_else(Bra_11$obj_hid_BWPER == 5, 1, 0)
Bra_11$construction_1971_1980 <- if_else(Bra_11$obj_hid_BWPER == 6, 1, 0)
Bra_11$construction_1981_1990 <- if_else(Bra_11$obj_hid_BWPER == 7, 1, 0)
Bra_11$construction_1991_2000 <- if_else(Bra_11$obj_hid_BWPER == 8, 1, 0)
Bra_11$construction_2001_later <- if_else(Bra_11$obj_hid_BWPER == 9, 1, 0)

# house type dummies: base is semi-detached house
Bra_11$corner_house <- if_else(Bra_11$obj_hid_TYPE == 3, 1, 0)
Bra_11$terraced_house <- if_else(Bra_11$obj_hid_TYPE == 2, 1, 0)
Bra_11$row_house <- if_else(Bra_11$obj_hid_TYPE == 1, 1, 0)
Bra_11$detached_house <- if_else(Bra_11$obj_hid_TYPE == 5, 1, 0)

# monument is already a dummy

# apartment type dummies: base is ground floor
Bra_11$two_floor_apartment <- if_else(Bra_11$obj_hid_SOORTAPP == 7, 1, 0)
Bra_11$upstairs_apartment <- if_else(Bra_11$obj_hid_SOORTAPP == 2, 1, 0)
Bra_11$maisonnette_apartment <- if_else(Bra_11$obj_hid_SOORTAPP == 3, 1, 0)
Bra_11$care_apartment <- if_else(Bra_11$obj_hid_SOORTAPP == 6, 1, 0)
Bra_11$gallery_apartment <- if_else(Bra_11$obj_hid_SOORTAPP == 4 | 5, 1, 0)

# isnieuwbouw is already a dummy

# basement dummy
Bra_11$basement <- if_else(Bra_11$obj_hid_KELDER >= 0, 1, 0)
# lift is already a dummy

# apartment quality dummy: base is apart_quality_regular
Bra_11$apart_quality_simple <- if_else(Bra_11$obj_hid_KWALITEIT == 0, 1, 0)
Bra_11$apart_quality_luxurious <- if_else(Bra_11$obj_hid_KWALITEIT == 2, 1, 0)


# combine zolder and vlier into one attic dummy variable
Bra_11$attic <- if_else(Bra_11$obj_hid_ZOLDER == 1 | Bra_11$obj_hid_VLIER == 1, 1, 0)

# parking dummy: base is no parking (all parking option combines, e.g. garage, parking lot, multi-level, etc.)
Bra_11$parking <- if_else(Bra_11$obj_hid_PARKEER == 0, 0, 1)

# balcony dummy: base is no balcony
Bra_11$balcony <- if_else(Bra_11$obj_hid_NBALKON >= 1, 1, 0)

# roof terrace dummy 
Bra_11$roof_terrace <- if_else(Bra_11$obj_hid_NDAKTERRAS >= 1, 1, 0)

# garden dummy
Bra_11$garden <- if_else(Bra_11$obj_hid_TUINLIG == 0, 0, 1)

# garden good location dummy (south incl SW & SE)
Bra_11$garden_south <- if_else(Bra_11$obj_hid_TUINLIG == 4 | 5 | 6, 1, 0)

# heating / utility dummies: base is no heating
Bra_11$ac_solar <- if_else(Bra_11$obj_hid_VERW == 3, 1, 0)
Bra_11$gas_coal <- if_else(Bra_11$obj_hid_VERW == 1, 1, 0)
Bra_11$central_heating <- if_else(Bra_11$obj_hid_VERW == 2, 1, 0)

# location dummies
Bra_11$city_centre <- if_else(Bra_11$obj_hid_LIGCENTR == 3, 1, 0)
Bra_11$quite_road <- if_else(Bra_11$obj_hid_LIGDRUKW == 0, 1, 0)
Bra_11$busy_road <- if_else(Bra_11$obj_hid_LIGDRUKW == 2, 1, 0)

# nature location dummies
Bra_11$free_view <- if_else(Bra_11$obj_hid_LIGMOOI == 4, 1, 0)
Bra_11$forest <- if_else(Bra_11$obj_hid_LIGMOOI == 1, 1, 0)
Bra_11$water <- if_else(Bra_11$obj_hid_LIGMOOI == 2, 1, 0)
Bra_11$park <- if_else(Bra_11$obj_hid_LIGMOOI == 3, 1, 0)

# new dataframe including relevant variables for the hedonic regression
Bra_12 <- Bra_11[,-c(9,10,12,14,18,20,24,26,29,35,39,40,41,42)]

# rename colunm for regressions
colnames(Bra_12)[colnames(Bra_12) == "obj_hid_M2"] <- "m2"
colnames(Bra_12)[colnames(Bra_12) == "obj_hid_ISNIEUWBOUW"] <- "new"
colnames(Bra_12)[colnames(Bra_12) == "obj_hid_LIFT"] <- "lift"
colnames(Bra_12)[colnames(Bra_12) == "obj_hid_NVERDIEP"] <- "n_floors"
colnames(Bra_12)[colnames(Bra_12) == "obj_hid_NKAMERS"] <- "n_rooms"
colnames(Bra_12)[colnames(Bra_12) == "obj_hid_MONUMENT"] <- "monument"
colnames(Bra_12)[colnames(Bra_12) == "obj_hid_NBADK"] <- "n_bathrooms"
colnames(Bra_12)[colnames(Bra_12) == "obj_hid_ONBI"] <- "maintenance_in"
colnames(Bra_12)[colnames(Bra_12) == "obj_hid_ONBU"] <- "maintenance_out"
colnames(Bra_12)[colnames(Bra_12) == "obj_hid_ISOL"] <- "n_isolation"
colnames(Bra_12)[colnames(Bra_12) == "obj_hid_INHOUD"] <- "volume"
colnames(Bra_12)[colnames(Bra_12) == "obj_hid_PERCEEL"] <- "plot_area"

# hedonic regression using nvm dataset variables only (excl. heat stress)

reg1 <- lm(lprice ~ m2 + n_rooms + n_floors + n_bathrooms + apartment + construction_1500_1905  + 
             construction_1931_1944 + construction_1945_1959 + construction_1960_1970 + construction_1971_1980 + 
             construction_1981_1990 + construction_1991_2000 + construction_2001_later + new + corner_house + 
             terraced_house + row_house + detached_house + two_floor_apartment + upstairs_apartment +
             maisonnette_apartment + care_apartment + gallery_apartment + lift + basement + balcony +
             roof_terrace + attic + monument + apart_quality_simple + apart_quality_luxurious + ac_solar + 
             gas_coal + central_heating + parking + garden + garden_south + city_centre + quite_road + 
             busy_road + free_view + forest + water + park, data = Bra_12)
summary(reg1)
stargazer(reg1, type = "html", out = "reg1.htm")

#### try the regression but with fixed-effects
gc()
memory.limit(9999999999)
fit <-lm(Y ~ X)
gc() 


# remove duplicate post codes with data to create a data frame for the fixxed effects interaction
Bra_13<-Bra_12 %>% distinct(obj_hid_POSTCODE, date, .keep_all = TRUE)

################################################################################################################################################################################################################################################################################################################################################################################################################################################################################################################################################################################################################################################################################################################################################################ LET'S SAVE Bra_13 so we don't have to load the whole thing everytime

save(Bra_13, file = "data.Rdata")

load(file = "data.Rdata")


#create the data frame for the fixed effects interaction
femod.p<-pdata.frame(Bra_13, index = c("obj_hid_POSTCODE", "date"))

#run the FE
femod<-plm(lprice ~ m2 + n_rooms + n_floors + n_bathrooms + apartment + construction_1500_1905  + 
             construction_1931_1944 + construction_1945_1959 + construction_1960_1970 + construction_1971_1980 + 
             construction_1981_1990 + construction_1991_2000 + construction_2001_later + new + corner_house + 
             terraced_house + row_house + detached_house + two_floor_apartment + upstairs_apartment +
             maisonnette_apartment + care_apartment + gallery_apartment + lift + basement + balcony +
             roof_terrace + attic + monument + apart_quality_simple + apart_quality_luxurious + ac_solar + 
             gas_coal + central_heating + parking + garden + garden_south + city_centre + quite_road + 
             busy_road + free_view + forest + water + park , data=femod.p, model = "within")
summary(femod)
library(stargazer)
stargazer(femod,title ="Variable descriptive statistics and output parameters equation", covariate.labels = c("Size in m2 (log)","Number of Rooms", "Number of Floors", "Number of Bathrooms", "Apartment", "Construction 1931-1944", "Construction 1945-1959", "Construction 1960-1970", "Construction 1971-1980", "Construction 1981-1990", "Construction 1991-2000", "New", "Corner House", "Terraced House","Row House", "Detached House", "Two-Floor Apartment", "Upstairs Apartment", "Maisonnette", "D: Lift", "D: Basement", "D: Balcony", "D: Roof Terrace", "D:Attic", "D: Monument", "D: Simple Apartment", "D: Luxurious Apartment", "D: AC/Solar", "D: Gas Coal", "D: Central Heating", "D: Parking", "D: Garden","City Centre", "Quite Road", "Busy Road", "Free View", "Forest", "Water", "Park"),   type = "html", out = "reg1.htm", no.space=TRUE, add.lines = list(c("Year and Zip Code Fixed-Effects", "Yes")), single.row = TRUE)


summary(Bra_13)


## create summary statistics of a few variables to put on the data
library(gtsummary)

trial2<-Bra_13 %>% select(obj_hid_TRANSACTIEPRIJS, m2 , n_rooms, n_bathrooms , ac_solar , 
             gas_coal , central_heating, obj_prov_ID)


### rename province to actual province name
trial2$obj_prov_ID<-as.character(trial2$obj_prov_ID)
trial2$obj_prov_ID[trial2$obj_prov_ID == '7'] <- "Utrecht"
trial2$obj_prov_ID[trial2$obj_prov_ID == '8'] <- "Noord-Holland"
trial2$obj_prov_ID[trial2$obj_prov_ID == '9'] <- "Zuid-Holland"


table1 <- tbl_summary(trial2)
table1

gt::tab_options(table.font.names = "Times New Roman")

table2<-tbl_summary(trial2,
                    by=obj_prov_ID,
                    label = list(m2 ~" m2", obj_hid_TRANSACTIEPRIJS ~"Price", n_rooms~ "Number of Rooms", n_bathrooms~"Number of Bathrooms", ac_solar~"AC/Solar", gas_coal~"Gas/Coal", central_heating~"Central Heating")) 

table2

table3<-trial2 %>%
  tbl_summary(by =
                obj_prov_ID,
              label = list(m2 ~" m2", obj_hid_TRANSACTIEPRIJS ~"Price", n_rooms~ "Number of Rooms", n_bathrooms~"Number of Bathrooms", ac_solar~"AC/Solar", gas_coal~"Gas/Coal", central_heating~"Central Heating"))%>%
  as_gt()%>%
  gt::tab_options(table.font.names = "Times New Roman")%>%
  as_flex_table()%>%
  flextable::save_as_docx()
table3
### save for word file

```

#####TRY TO MAP AC IN HOUSES BEFORE 2003 AND AFTER

```{r}
#filter for the date first between 2000 and 2003 right after the heat wave
ac2003<- filter(Bra_13, Bra_13$obj_hid_DATUM_AANMELDING > "2000-01-01" & Bra_13$obj_hid_DATUM_AANMELDING <"2003-09-01")

#create data frame with only ac_solar variable

ac2003_01<-ac2003[84]
# we get a total of 104,851 observations

sum(ac2003_01$ac_solar==1)

#only 18 houses transacted in this dataset had AC/Solar

### now lets do the same but for the period 3 years after the heat wave

acafter<- filter(Bra_13, Bra_13$obj_hid_DATUM_AANMELDING > "2003-09-01" & Bra_13$obj_hid_DATUM_AANMELDING <"2006-09-01")

ac2003_01_after<-acafter[84]


sum(ac2003_01_after$ac_solar==1)
#only 11 houses transacted after that had AC

ac_count<-Bra_13[46]
sum(ac_count$obj_hid_VERW==3)
#only 102 houses total have AC in the whole dataset

sum(Bra_1$obj_hid_VERW==3)

##check the number of ground floor apartments
sum(Bra_13$obj_hid_SOORTWONING==21)
## we get 557 groundfloor apartments

#check the number of upstair apartmetnts
sum(Bra_13$obj_hid_SOORTWONING==22)
#We get 2407 upstair apartments


#check the number of healthcare houses
sum(Bra_13$obj_hid_SOORTWONING==26)
#just 1
```

##♠REMOVE SPACES FROM POSTAL CODE

```{r}
# remove blank between postalcode
sentenceString <- Bra_13$obj_hid_POSTCODE
searchString <- " "
replacementString <- ""
sentenceString = gsub(searchString,replacementString,sentenceString)
Bra_13$obj_hid_POSTCODE <- sentenceString


##########export file to csv addresses##########


write.csv(Bra_13[8], "test.csv")
```

##try to open Climate Impact Atlas map

```{r}
install.packages("raster")
install.packages("rgdal")
library(rgdal)
library(raster)
##create file
grey <- raster("cas.tif")

#check the map
plot(grey)

#summary from the thing
summary(grey)
```


#### TEST RUN WITH A FEW OBS

```{r}
##upload the data
library(readxl)
latlong <- read_excel("latlong.xlsx", col_types = c("text", 
    "text", "numeric", "numeric"))
#remove the full address column
latlong$full_address<-NULL
### join the data with the dataset

##first create test dataset

test_bra<-Bra_13[1:3722, ]

##try to join the data
test_bra$postalcode<-latlong$`"obj_hid_POSTCODE"`
test_bra$lat<-latlong$lat
test_bra$long<-latlong$long

######## Use tutorial to understand spatial data ########
## http://www.seascapemodels.org/rstats/rspatial/2015/06/22/R_Spatial_course.html# 
# Turning points into a spatial object
coordinates(test_bra) <- ~long + lat
coordinates(test_bra)
spplot(test_bra)
plot(test_bra)

# Transform to local projection
proj4string(test_bra) <- "+proj=longlat +ellps=GRS80 +no_defs"
myproj <- "+proj=sterea +lat_0=52.15616055555555 +lon_0=5.38763888888889 +k=0.9999079 +x_0=155000 +y_0=463000
+ellps=bessel +towgs84=565.2369,50.0087,465.658,-0.406857,0.350733,-1.87035,4.0812 +units=m +no_defs"

datutm <- spTransform(test_bra, CRS(myproj))
coordinates(datutm)

a4250<-raster("35.tif")
plot(a4250)  
spplot(a4250)
  

#### test youtube
testlat<-raster("randstad.tif")
plot(testlat)
spplot(testlat)
testlat
p=as(testlat@extent, "SpatialPolygons")
pts=spsample(p, n=50000000, "random")
pts$value=runif(50000000, min=36, max = 51)
dataframe=as.data.frame(pts)
```



###MERGE TWO DATASETS BASED ON LAT LONG

```{r}
## import dataset with post codes + lat and long

library(readxl)
unique <- read_excel("Coordinates/unique.xlsx")



#### that did not work: let's try to remove some last digits

unique$realx<-substr(unique$x,1,6)
unique$realy<-substr(unique$y,1,7)


###• do the same for the raster

dataframe$realx<-substr(dataframe$x,1,6)
dataframe$realy<-substr(dataframe$y,1,7)

save(dataframe, file = "dataframe.Rdata")

load(file = "dataframe.Rdata")
##let's try to merge again
total<-merge(dataframe, unique, by = c("realx", "realy"))
###some observations

total$x.x<-NULL
total$y.x<-NULL
total$x.y<-NULL
total$y.y<-NULL

```


#### MERGE THE FINAL DATA SET WITH TEMP DATA AND ALL OTHER CHARAHCTHERISTICS

```{r}
###first we need to rename so both have zip_code as common variable
colnames(Bra_13)[colnames(Bra_13) == "obj_hid_POSTCODE"] <- "zip_code"


## then we need to remove the space in between the numbers and letter

sentenceString <- Bra_13$zip_code
searchString <- " "
replacementString <- ""
sentenceString = gsub(searchString,replacementString,sentenceString)
Bra_13$zip_code <- sentenceString


### Now I think we have everything

first<-merge(total, Bra_13, by = "zip_code")

###let's remove some duplicates

second<-distinct(first, first$obj_ID, .keep_all = TRUE)

### let's try first regression

#create the data frame for the fixed effects interaction
femod.p<-pdata.frame(second, index = c("zip_code", "date"))

###let's try to add random numbers

femod.p$random<-runif(77214, min=0.0000001, max = 0.000001)

femod.p$newvalue<-femod.p$value+femod.p$random

femod.p$newvalue<-as.numeric(femod.p$newvalue)

femod.p$lognewvalue<-log(femod.p$newvalue)

##do I need to standardize the variable?

femod.p$scale<-(femod.p$newvalue-mean(femod.p$newvalue))/sd(femod.p$newvalue)

#run the FE
femod<-plm(lprice ~ newvalue + m2 + n_rooms + n_floors + n_bathrooms + apartment + construction_1500_1905  + 
             construction_1931_1944 + construction_1945_1959 + construction_1960_1970 + construction_1971_1980 + 
             construction_1981_1990 + construction_1991_2000 + construction_2001_later + new + corner_house + 
             terraced_house + row_house + detached_house + two_floor_apartment + upstairs_apartment +
             maisonnette_apartment + care_apartment + gallery_apartment + lift + basement + balcony +
             roof_terrace + attic + monument + apart_quality_simple + apart_quality_luxurious + ac_solar + 
             gas_coal + central_heating + parking + garden + garden_south + city_centre + quite_road + 
             busy_road + free_view + forest + water + park, data=femod.p, model = "within")
summary(femod)

stargazer(femod,
          title="Temperature and Price Effects",
          dep.var.caption = "Property Transaction Price",
          dep.var.labels = "Price in Log",
          omit = c("construction_1931_1944", "construction_1945_1959",
                   "construction_1960_1970", "construction_1971_1980",
                   "construction_1981_1990", "construction_1991_2000",
                   "lift", "basement", "balcony", "roof_terrace", "monument", "apart_quality_simple", "apart_quality_luxurious", "parking", "garden", "city_centre", "quite_road", "busy_road", "free_view", "forest", "water", "park"),
          covariate.labels = c("Temperature 2050", "m2", "Number of Rooms", "Number of Floors", "Number of Bathrooms", "Apartment", "New Dwelling", "Corner House", "Terraced House", "Row House", "Detached House", "Two Floor Apartment", "Upstairs Apartment", "Maisonnette", "Attic", "AC/Solar", "Gas/Coal", "Central Heating"),
          type = "html", add.lines = list(c("Year and Zip Code Fixed-Effects", "Yes")),
          no.space = TRUE, single.row=TRUE,
          out = "stargazer.htm")

#### let's try the same but without temperature

femod1<-plm(lprice ~ m2 + n_rooms + n_floors + n_bathrooms + apartment + construction_1500_1905  + 
             construction_1931_1944 + construction_1945_1959 + construction_1960_1970 + construction_1971_1980 + 
             construction_1981_1990 + construction_1991_2000 + construction_2001_later + new + corner_house + 
             terraced_house + row_house + detached_house + two_floor_apartment + upstairs_apartment +
             maisonnette_apartment + care_apartment + gallery_apartment + lift + basement + balcony +
             roof_terrace + attic + monument + apart_quality_simple + apart_quality_luxurious + ac_solar + 
             gas_coal + central_heating + parking + garden + garden_south + city_centre + quite_road + 
             busy_road + free_view + forest + water + park, data=femod.p, model = "within")

summary(femod1)

stargazer(femod1,
          title="Temperature and Price Effects",
          dep.var.caption = "Property Transaction Price",
          dep.var.labels = "Price in Log",
          omit = c("construction_1931_1944", "construction_1945_1959",
                   "construction_1960_1970", "construction_1971_1980",
                   "construction_1981_1990", "construction_1991_2000",
                   "lift", "basement", "balcony", "roof_terrace", "monument", "apart_quality_simple", "apart_quality_luxurious", "parking", "garden", "city_centre", "quite_road", "busy_road", "free_view", "forest", "water", "park"),
          covariate.labels = c("m2", "Number of Rooms", "Number of Floors", "Number of Bathrooms", "Apartment", "New Dwelling", "Corner House", "Terraced House", "Row House", "Detached House", "Two Floor Apartment", "Upstairs Apartment", "Maisonnette", "Attic", "AC/Solar", "Gas/Coal", "Central Heating"),
          type = "html", add.lines = list(c("Year and Zip Code Fixed-Effects", "Yes")),
          no.space = TRUE, single.row=TRUE,
          out = "stargazer1.htm")


###☺ NO CHANGE IN ANY OF THE VARIABLES, TEMPERATURE REALLY IS USELESS
```


################################################################################################################################################################################ HEAT WAVE STUDY ##########################


```{r}
# create dummy variables for transactions that happened during heatwave in 2015

# 1 quarter first

femod.p$post_quarter<-ifelse(femod.p$obj_hid_DATUM_AFMELDING >= "2015-07-05" & femod.p$obj_hid_DATUM_AFMELDING < "2015-10-05", 1, 0)

# half-year

femod.p$post_half<-ifelse(femod.p$obj_hid_DATUM_AFMELDING >= "2015-07-05" & femod.p$obj_hid_DATUM_AFMELDING < "2016-01-05", 1, 0)

# one-year

femod.p$post_year<-ifelse(femod.p$obj_hid_DATUM_AFMELDING >= "2015-07-05" & femod.p$obj_hid_DATUM_AFMELDING < "2016-07-05", 1, 0)

#two- year

femod.p$post_two_year<-ifelse(femod.p$obj_hid_DATUM_AFMELDING >= "2015-07-05" & femod.p$obj_hid_DATUM_AFMELDING < "2017-07-05", 1, 0)


heat_wave2015<-plm(lprice ~ newvalue + m2 + n_rooms + n_floors + n_bathrooms + apartment + construction_1500_1905  + 
             construction_1931_1944 + construction_1945_1959 + construction_1960_1970 + construction_1971_1980 + 
             construction_1981_1990 + construction_1991_2000 + construction_2001_later + new + corner_house + 
             terraced_house + row_house + detached_house + two_floor_apartment + upstairs_apartment +
             maisonnette_apartment + care_apartment + gallery_apartment + lift + basement + balcony +
             roof_terrace + attic + monument + apart_quality_simple + apart_quality_luxurious + ac_solar + 
             gas_coal + central_heating + parking + garden + garden_south + city_centre + quite_road + 
             busy_road + free_view + forest + water + park + post_two_year, data=femod.p, model = "within")
summary(heat_wave2015)
```


##### try the 2013 heat wave - SIGNIFICANT AND NEGATIVE IMPACT

```{r}
# 1 quarter first
femod.p$post_quarter_2013<-ifelse(femod.p$obj_hid_DATUM_AFMELDING >= "2013-07-27" & femod.p$obj_hid_DATUM_AFMELDING < "2013-10-27", 1, 0)

### half-year

femod.p$post_half_2013<-ifelse(femod.p$obj_hid_DATUM_AFMELDING >= "2013-07-27" & femod.p$obj_hid_DATUM_AFMELDING < "2014-01-27", 1, 0)

###æ one-year

femod.p$post_one_2013<-ifelse(femod.p$obj_hid_DATUM_AFMELDING >= "2013-07-27" & femod.p$obj_hid_DATUM_AFMELDING < "2014-07-27", 1, 0)

### two-year

femod.p$post_two_2013<-ifelse(femod.p$obj_hid_DATUM_AFMELDING >= "2013-07-27" & femod.p$obj_hid_DATUM_AFMELDING < "2015-07-27", 1, 0)

### Run regression
heat_wave2013<-plm(lprice ~ newvalue + m2 + n_rooms + n_floors + n_bathrooms + apartment + construction_1500_1905  + 
             construction_1931_1944 + construction_1945_1959 + construction_1960_1970 + construction_1971_1980 + 
             construction_1981_1990 + construction_1991_2000 + construction_2001_later + new + corner_house + 
             terraced_house + row_house + detached_house + two_floor_apartment + upstairs_apartment +
             maisonnette_apartment + care_apartment + gallery_apartment + lift + basement + balcony +
             roof_terrace + attic + monument + apart_quality_simple + apart_quality_luxurious + ac_solar + 
             gas_coal + central_heating + parking + garden + garden_south + city_centre + quite_road + 
             busy_road + free_view + forest + water + park + post_one_2013, data=femod.p, model = "within")
summary(heat_wave2013)
```

########################################################################################################################################################################### SAVE FEMOD.P DATAFRAME ########################

```{r}
save(femod.p, file = "femod.Rdata")

load(file = "femod.Rdata")
```


###### TRY THE 2003 HEAT WAVE

```{r}
### one quarter
heat_wave2003_quarter<-plm(lprice ~ newvalue + m2 + n_rooms + n_floors + n_bathrooms + apartment + construction_1500_1905  + 
             construction_1931_1944 + construction_1945_1959 + construction_1960_1970 + construction_1971_1980 + 
             construction_1981_1990 + construction_1991_2000 + construction_2001_later + new + corner_house + 
             terraced_house + row_house + detached_house + two_floor_apartment + upstairs_apartment +
             maisonnette_apartment + care_apartment + gallery_apartment + lift + basement + balcony +
             roof_terrace + attic + monument + apart_quality_simple + apart_quality_luxurious + ac_solar + 
             gas_coal + central_heating + parking + garden + garden_south + city_centre + quite_road + 
             busy_road + free_view + forest + water + park + post_quarter_2003, data=femod.p, model = "within")
summary(heat_wave2003_quarter)

###half-year

heat_wave2003_half<-plm(lprice ~ newvalue + m2 + n_rooms + n_floors + n_bathrooms + apartment + construction_1500_1905  + 
             construction_1931_1944 + construction_1945_1959 + construction_1960_1970 + construction_1971_1980 + 
             construction_1981_1990 + construction_1991_2000 + construction_2001_later + new + corner_house + 
             terraced_house + row_house + detached_house + two_floor_apartment + upstairs_apartment +
             maisonnette_apartment + care_apartment + gallery_apartment + lift + basement + balcony +
             roof_terrace + attic + monument + apart_quality_simple + apart_quality_luxurious + ac_solar + 
             gas_coal + central_heating + parking + garden + garden_south + city_centre + quite_road + 
             busy_road + free_view + forest + water + park + post_half_2003, data=femod.p, model = "within")
summary(heat_wave2003_half)

### one-year

heat_wave2003_one<-plm(lprice ~ newvalue + m2 + n_rooms + n_floors + n_bathrooms + apartment + construction_1500_1905  + 
             construction_1931_1944 + construction_1945_1959 + construction_1960_1970 + construction_1971_1980 + 
             construction_1981_1990 + construction_1991_2000 + construction_2001_later + new + corner_house + 
             terraced_house + row_house + detached_house + two_floor_apartment + upstairs_apartment +
             maisonnette_apartment + care_apartment + gallery_apartment + lift + basement + balcony +
             roof_terrace + attic + monument + apart_quality_simple + apart_quality_luxurious + ac_solar + 
             gas_coal + central_heating + parking + garden + garden_south + city_centre + quite_road + 
             busy_road + free_view + forest + water + park + post_one_2003, data=femod.p, model = "within")
summary(heat_wave2003_one)



save(Bra_13, file = "bra_13_updated.Rdata")

load(file = "bra_13_updated.Rdata")

save(femod.p, file = "femod.p_updated.Rdata")

load(file = "femod.p_updated.Rdata")

save(first, file = "first.Rdata")
```

####### Maybe try to divide by heat stress levels

```{r}
femod.p$level1<-ifelse(femod.p$newvalue >= '36' & femod.p$newvalue < '41', 1, 0)

femod.p$level1<-as.numeric(femod.p$level1)

str(femod.p$level1)

medium_risk<-plm(lprice ~ level1  +m2 + n_rooms + n_floors + n_bathrooms + apartment + construction_1500_1905  + 
             construction_1931_1944 + construction_1945_1959 + construction_1960_1970 + construction_1971_1980 + 
             construction_1981_1990 + construction_1991_2000 + construction_2001_later + new + corner_house + 
             terraced_house + row_house + detached_house + two_floor_apartment + upstairs_apartment +
             maisonnette_apartment + care_apartment + gallery_apartment + lift + basement + balcony +
             roof_terrace + attic + monument + apart_quality_simple + apart_quality_luxurious + ac_solar + 
             gas_coal + central_heating + parking + garden + garden_south + city_centre + quite_road + 
             busy_road + free_view + forest + water + park, data=femod.p, model = "within")
summary(medium_risk)
```











